%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.
%Version for spanish users, by dgarhdez
\PassOptionsToPackage{colorlinks=true, linkcolor=blue, filecolor=blue, urlcolor=blue, citecolor=blue}{hyperref}

\documentclass[10pt,a4paper,roman]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')
\usepackage[english, spanish]{babel}
\hyphenation{}
\usepackage{eurosym}
\usepackage{threeparttable} % allow the use of footnote within tables
\usepackage{subcaption}
\usepackage{url}
\usepackage{xurl} % allow line breaks anywhere in URL string
\usepackage{xr} 
\externaldocument{supplementarymaterial}

%to add the number to the lines
\usepackage{lineno}
\modulolinenumbers[5]


\modulolinenumbers[1]
\usepackage{amsmath}
\usepackage[T1]{fontenc}
\usepackage{siunitx}
\usepackage{mathrsfs}
\usepackage{eurosym}
\usepackage[europeanresistors,americaninductors]{circuitikz}
\usepackage{adjustbox}
\usepackage{xspace}
\usepackage{caption}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{threeparttable}
\usepackage{multicol, multirow}
\usepackage{float}
\usepackage{graphicx,dblfloatfix}
\usepackage{csvsimple}
\usepackage{amssymb}% http://ctan.org/pkg/amssymb
\usepackage{pifont}% http://ctan.org/pkg/pifont
\usepackage{tikzsymbols}
\usepackage{textcomp}
\usepackage{etoolbox}
\usepackage{longtable}
\usepackage{csquotes}
\usepackage{ragged2e}

% Define dark blue color
\usepackage{xcolor}
\definecolor{darkblue}{rgb}{0,0,0.5}

\usepackage[numbers,sort&compress]{natbib}

% [The rest of your preamble content, if any]

%% new commands
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\newcommand{\ubar}[1]{\text{\b{$#1$}}}
\newcommand*\OK{\ding{51}}
\newcolumntype{L}{>{\begin{math}}l<{\end{math}}}%
\newcolumntype{C}{>{\begin{math}}c<{\end{math}}}%
%\renewcommand*\nompostamble{\end{multicols}}
\newcommand{\specialcell}[2][c]{%
\begin{tabular}[#1]{@{}l@{}}#2\end{tabular}}
\def\co{CO${}_2$}
\def\el{${}_{\textrm{el}}$}
\def\th{${}_{\textrm{th}}$}
\newcommand{\mwth}{\ \officialeuro /MWh$_{\text{th}}$}
\newcommand{\mwh}{\ \officialeuro /MWh\ }
\newcommand{\mw}{\ \officialeuro /MW\ }
\newcommand{\kw}{\ \officialeuro /kW}
\newcommand{\kwe}{\ \officialeuro /kW$_{\text{elec}}$\ }
\newcommand{\kwee}{\ \officialeuro /kW$_{\text{elec}}$}
\newcommand{\mwhend}{\ \officialeuro /MWh}
\newcommand{\scenario}[1]{\textbf{\hyperlink{retro+}{#1}}}
\newcommand{\budget}[1]{+{#1}$^\text{o}$C budget}
\newcommand{\ce}[1]{+{#1}$^\text{o}$C}
\newcommand{\todo}[1]{\textcolor{red}{TODO: #1}}
% To add an 'S' prefix to a reference
\newcommand*\sref[1]{%
S\ref{#1}}


% moderncv themes
\moderncvstyle{classic}                            % style
\moderncvcolor{black}                              % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Bobby}{Xiong}
\title{The role of Projects of Common Interest in reaching Europe's energy policy targets}                     
\address{Dep. of Digital Transformation in Energy Systems\\Technische Universität Berlin\\ Einsteinufer 25, 10587 Berlin, Germany}
\email{xiong@tu-berlin.de}  

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bib\usepackage[numbers]{natbib}liographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%-----       letter       ---------------------------------------------------------
% recipient data
\recipient{To}{Editorial Board of IOP Environmental Research Letters\vspace{-0.25cm}}
\date{\selectlanguage{english}\today}

% subject
\subject{Justification statement for manuscript submission\vspace{-0.6cm}}

\opening{Dear Prof. Kammen}
\makelettertitle
\justifying
In the following, we provide brief justification statements accompanying our manuscript titled \textit{\enquote{The role of Projects of Common Interest in reaching Europe's energy policy targets}}.

\textbf{1. Key results and findings} 
\begin{itemize}
    \item Investing in Projects of Common and Mutual Interest (PCI-PMI) boosts net social welfare and accelerates decarbonisation of hard-to-abate sectors.
    \item However, potential delays in hydrogen and CO$_2$ infrastructure commissioning can cause substantial economic regrets, adding up to €24.2 billion in annual costs.
    \item We identify pipeline candidates beyond the current PCI-PMI projects that have the potential to unlock additional welfare gains of €7-18 billion per year.
    \item Diversifying the technology portfolio through CO$_2$ infrastructure avoids lock-in to costly technologies, such as Direct Air Capture, and can reduce reliance by up to 136 Mt annually.
\end{itemize}

\textbf{2. Contributions to human efforts to address environmental global change} 

The findings of our study reduce uncertainty surrounding the `chicken-and-egg' dilemma in infrastructure investment --- whether to build ahead of demand or wait --- by quantifying economic and timing risks. This is especially important considering the high capital costs and long lead times of large-scale infrastructure planning. We provide policymakers and industry stakeholders with evidence that proactive investment is both feasible and economically advantageous, supporting a faster transition to a decarbonized energy system. 

\textbf{3. Relevance to researchers of other fields and regions}

Additionally, our findings inform researchers in other disciplines, such as regulatory policy, aiding the development of frameworks that facilitate timely infrastructure deployment. Insights from this European case study can also be adapted to other regions and sectors facing similar challenges.

\textbf{4. Publication in IOP Environmental Research Letters} 

Our study provides a data-driven foundation for aligning infrastructure policy with Europe's long-term decarbonisation goals, ensuring that strategic investments today yield systemic benefits tomorrow.  We believe it fits well with IOP ERL, being a leading journal in environmental research that integrates model-based assessments with policy relevance. Additionally, the open-source and fully reproducible scientific workflow of this research paper aligns closely with the journal’s commitment to transparency, reproducibility, and open access.

Kind regards,\\
Bobby Xiong (corresponding author), Prof. Dr. Tom Brown \& Dr. Iegor Riepin

\end{document}


